Group 5 Report

### 2022-08-03 Report/Group 5 report v2.Rmd
Image captions

```{r, echo=FALSE, fig.cap="Need caption", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Brns_items.png")
knitr::include_graphics("Images/OPX_items.png")
knitr::include_graphics("Images/Marriage.png")
```

>>>>

```{r, echo=FALSE, fig.cap="Need caption", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Brns_items1.png")
knitr::include_graphics("Images/OPX_items1.png")
knitr::include_graphics("Images/Marriage.png")
```
